Data preparation

### 2021-02-19 Analysis/01_data_preparation.Rmd
Added tip names

@@

## Re-saving the trees and saving the spaces
spaces_list <- list(psittaciformes  = cleaned_psita$data,
                    charadriiformes = cleaned_chara$data)
trees_list  <- list(psittaciformes  = cleaned_psita$tree,
                    charadriiformes = cleaned_chara$tree)
save(trees_list,  file = "../Data/Processed/trees_list.rda")
save(spaces_list, file = "../Data/Processed/spaces_list.rda")
```

>>>>

> Note

@@

## Re-saving the trees and saving the spaces
spaces_list <- list(psittaciformes  = cleaned_psita$data,
                    charadriiformes = cleaned_chara$data)

## Adding the node labels for each selected trees
psita_trees <- lapply(cleaned_psita$tree, function(tree) {tree$node.label <- paste0("n", 1:Nnode(tree)); return(tree)})
chara_trees <- lapply(cleaned_chara$tree, function(tree) {tree$node.label <- paste0("n", 1:Nnode(tree)); return(tree)})
class(psita_trees) <- class(chara_trees) <- "multiPhylo"

trees_list  <- list(psittaciformes  = psita_trees,
                    charadriiformes = chara_trees)

save(trees_list,  file = "../Data/Processed/trees_list.rda")
save(spaces_list, file = "../Data/Processed/spaces_list.rda")
```
